s.function

### 2023-03-20 src/la_ranks_n1.Rmd
all .png files

df <- bind_rows(df9610, df1112) %>% 
  filter(
    V1.domain < m,             # for multiple pc
    #V1.domain == n,           # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  #summarise(n = n()) %>%            # for multiple pc  
  summarise(n = sum(V1.domain)) %>% # for n == 1 
  ungroup()

@@

df <- df %>% left_join(la.names)
# source: https://geoportal.statistics.gov.uk/
```

## Ranks websites per firm t and 2012 only

@@

out.path <- paste0(path, "/outputs/ranks/web11_per_firm", t,"_2012_only95.png")

df %>% group_by(year) %>% 
  mutate(rank = rank(desc(n_by_firm))) %>% # or n_by_firm
  ungroup() %>% 
  filter(year==t | year == 2012) %>% 
  arrange(ladcd, year) %>% 
  group_by(ladcd) %>% 
  #mutate(diff_1st = -diff(rank))
  mutate(diff_1st = -(rank-lag(rank))) %>% 
  #ungroup() %>% summarise(q = quantile(abs(diff_1st), .95, na.rm = T)) 
  # t= 2000: q.95 = , q.9 = , q.1 = , q.05 = . **abs()**
  # t= 1996: q.95 = 243.625, q.9 = 191.5, q.1 = 11.5, q.05 = 6. **abs()**

  mutate(alpha = ifelse(abs(diff_1st) > 243.625, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

@@

```{r}
out.path <- paste0(path, "/outputs/ranks/web11_per_year.png")

@@

```{r}  
out.path <- paste0(path, "/outputs/ranks/web11_per_firm1996_2012_95.png")

df %>% group_by(year) %>% 
  mutate(rank = rank(desc(n_by_firm))) %>% # or n_by_firm
  ungroup() %>% 
  #filter(year==t | year == 2012) %>% 
  arrange(ladcd, year) %>% 
  group_by(ladcd) %>% 
  #mutate(diff_1st = -diff(rank))
  mutate(diff_1st = -(rank-lag(rank, n=16))) %>% 
  #ungroup() %>% summarise(q = quantile(abs(diff_1st), .95, na.rm = T)) 
  # t= 2000: q.95 = , q.9 = , q.1 = , q.05 = . **abs()**
  # t= 1996: q.95 = 243.625, q.9 = 191.5, q.1 = 11.5, q.05 = 6. **abs()**

  mutate(alpha = ifelse(abs(diff_1st) > 243.625, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

>>>>

df <- bind_rows(df9610, df1112) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  #summarise(n = n()) %>%            # for multiple pc  
  summarise(n = sum(V1.domain)) %>% # for n == 1 
  ungroup()

@@

df <- df %>% left_join(la.names)
# source: https://geoportal.statistics.gov.uk/
```
## Ranks websites per firm t and 2012 only

@@

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only05.png")

df %>% group_by(year) %>% 
  mutate(rank = rank(desc(n_by_firm))) %>% # or n_by_firm
  ungroup() %>% 
  filter(year==t | year == 2012) %>% 
  arrange(ladcd, year) %>% 
  group_by(ladcd) %>% 
  #mutate(diff_1st = -diff(rank))
  mutate(diff_1st = -(rank-lag(rank))) %>% 
  #ungroup() %>% summarise(q = quantile(abs(diff_1st), .95, na.rm = T)) 
  # t= 2000: q.95 = 199.5, q.9 = 168, q.1 = 7, q.05 = 3.75. **abs()**
  # t= 1996: q.95 = 257.125, q.9 = 232.25, q.1 = 17.75, q.05 = 6.875. **abs()**

  mutate(alpha = ifelse(abs(diff_1st) < 6.875, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

@@

```{r}
out.path <- paste0(path, "/outputs/ranks/web_per_year.png")

@@

```{r}  
out.path <- paste0(path, "/outputs/ranks/web_per_firm1996_2012_95.png")

df %>% group_by(year) %>% 
  mutate(rank = rank(desc(n_by_firm))) %>% # or n_by_firm
  ungroup() %>% 
  #filter(year==t | year == 2012) %>% 
  arrange(ladcd, year) %>% 
  group_by(ladcd) %>% 
  #mutate(diff_1st = -diff(rank))
  mutate(diff_1st = -(rank-lag(rank, n=16))) %>% 
  #ungroup() %>% summarise(q = quantile(abs(diff_1st), .95, na.rm = T)) 
  # t= 2000: q.95 = , q.9 = , q.1 = , q.05 = . **abs()**
  # t= 1996: q.95 = 257.125, q.9 = 232.25, q.1 = 17.75, q.05 = 6.875. **abs()**

  mutate(alpha = ifelse(abs(diff_1st) > 257.125, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

### 2023-03-20 src/s_la_per_firm_m11.Rmd
all .png files

df <- bind_rows(df9610, df1112) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  #summarise(n = n()) %>%            # for multiple pc  
  summarise(n = sum(V1.domain)) %>% # for n == 1 
  ungroup()

@@

xmid.uk <- tidy(fit) %>% filter(term=="xmid") %>% select(estimate) %>% as.numeric()

@@

path.out <- paste0(path, "/outputs/s_uk_per_firm.png")

df.country %>% 
  ggplot(aes(x = year, y = n) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df.country$year), breaks = df.country$year) +
  geom_vline(xintercept = 2003) +
  ylab("N. of websites / per firm") +
  ggtitle("S-curve, UK") +
  theme(plot.title = element_text(hjust = 0.5))

@@

a.la <- a.la %>% filter(term=="xmid") %>% 
  bind_cols(as.tibble(all.la)) %>% 
  #mutate(estimate = round(estimate, 0)) %>% 
  #summarise(r = range(r2))
  filter(p.value < 0.01 & 
         r2 > 0.9) %>%    # 376 / 376, all sig, 330 r2 > 0.9
  dplyr::select(ladcd, estimate, r2, std.error) %>%
  mutate(fast = ifelse(estimate < xmid.uk, "fast", "slow")) # it was 2003

@@

# plots
path.out <- paste0(path, "/outputs/s_lad_per_firm/lad_")

@@

  xmid_la <- pred %>% left_join(a.la) %>% filter(ladcd == i) %>% dplyr::select(estimate) %>% first()
  lines <- data.frame(
    intercepts = c(xmid.uk, xmid_la[1]), # it was 2003
    Xmid = c("UK", i)
  )

@@

```{r eval=F}
path.out <- paste0(path, "/data/temp/s_la_per_firm.csv")
write_csv(a.la, path.out)
```

>>>>

df <- bind_rows(df9610, df1112) %>% 
  filter(
    V1.domain < m,             # for multiple pc
    #V1.domain == n,           # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  #summarise(n = n()) %>%            # for multiple pc  
  summarise(n = sum(V1.domain)) %>% # for n == 1 
  ungroup()

@@

@@

path.out <- paste0(path, "/outputs/s_uk_per_firm_11.png")

df.country %>% 
  ggplot(aes(x = year, y = n) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df.country$year), breaks = df.country$year) +
  geom_vline(xintercept = 2002) +
  ylab("N. of websites / per firm") +
  ggtitle("S-curve, UK") +
  theme(plot.title = element_text(hjust = 0.5))

@@

a.la <- a.la %>% filter(term=="xmid") %>% 
  bind_cols(as.tibble(all.la)) %>% 
  #mutate(estimate = round(estimate, 0)) %>% 
  #summarise(r = range(r2))
  filter(p.value < 0.01 & 
         r2 > 0.9) %>%    # 376 / 376, all sig, 330 r2 > 0.9
  dplyr::select(ladcd, estimate, r2, std.error) %>%
  mutate(fast = ifelse(estimate < 2002, "fast", "slow"))

@@

# plots
path.out <- paste0(path, "/outputs/s_la_er_firm_m11/lad11_")

@@

  xmid_la <- pred %>% left_join(a.la) %>% filter(ladcd == i) %>% dplyr::select(estimate) %>% first()
  lines <- data.frame(
    intercepts = c(2002, xmid_la[1]),
    Xmid = c("UK", i)
  )

@@

```{r eval=F}
path.out <- paste0(path, "/data/temp/s_la_per_firm_11.csv")
write_csv(a.la, path.out)
```
